% LaTeX resume using res.cls
\documentclass[margin]{res}
\usepackage{lipsum}
\usepackage{datetime}
\usepackage{hyperref}

\begin{document}

\moveleft.5\hoffset\centerline{\huge \bf Mihai-Cristian Fufezan}
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
\moveleft.36\hoffset\centerline{{\bf Email}: \href{mailto:mihai@fufexan.net}{mihai@fufexan.net} $\diamond $\hspace{1mm}{\bf GitHub}: \href{https://github.com/fufexan}{github.com/fufexan}}
\moveleft.5\hoffset\centerline{{\bf LinkedIn:} \href{https://linkedin.com/in/mihai-fufezan}{linkedin.in/mihai-fufezan}}


\begin{resume}
  \thispagestyle{empty}
  \section{PERSONAL STATEMENT}
  Second year Computer Engineering student with a passion for developing great programs and managing systems. Enjoys finding the intersection between fast, correct, and elegant code.

  \section{EXPERIENCE}
  {\bf NixOS Foundation - Contracting} \hfill \textit{2022}\\
  \begin{itemize}
    \item Took part in a team of participants to package NGI (Next Generation Internet) applications with Nix for \href{https://summer.nixos.org}{\textbf{Summer of Nix}} program, as well as developing dream2nix and improving the overall Nix/OS documentation.
    \item Used \href{https://github.com/nix-community/dream2nix}{\textbf{dream2nix}} to package projects written in JavaScript and Python.
    \item Contributed to the development of \href{https://github.com/nix-community/dream2nix}{\textbf{dream2nix}}.
    \item Improved documentation of several areas of the \href{https://nixos.wiki}{\textbf{NixOS Wiki}}.
    \item Created publicly-available flakes accessible on the \href{https://github.com/ngi-nix}{\textbf{NGI-Nix repo}}.
  \end{itemize}

  {\bf NixOS Foundation - Contracting} \hfill \textit{2021}\\
  \begin{itemize}
    \item Took part in a team of 5 fulltime contractors to package 20+ NGI (Next Generation Internet) applications with Nix for \href{https://summer.nixos.org}{\textbf{Summer of Nix}} program.
    \item Packaged programs on my own, as well as collaborating with others.
    \item Learned different techniques of packaging projects written in the following languages and familiarized myself with their build tools: C, JavaScript, OCaml, Python.
    \item Created publicly-available flakes accessible on the \href{https://github.com/ngi-nix}{\textbf{NGI-Nix repo}}.
  \end{itemize}

  {\bf Digital Nation - Apprenticeship} \hfill \textit{2019 - 2020}\\
  \begin{itemize}
    \item Participated as an apprentice in the \href{https://generatiatech.ro}{\textbf{Generația Tech}} program.
    \item Learned PHP development using WordPress themes \& plugins, under the guidance of skilled mentors.
    \item Learned JavaScript back-end and front-end development, Firebase management and integration.
    \item Was local ambassador for the Alba county regional group. Participated in team management, administration, logistics.
  \end{itemize}

  \section{SKILLS}
  {\bf Languages:} C/C++, Bash, Java, JavaScript, Nix, PHP, Python\\
  {\bf Databases:} MySQL\\
  {\bf Version Control:} Git\\
  {\bf Build Tools:} Meson, Nix\\
  {\bf Operating systems:} Linux\\
  {\bf DevOps:} NixOS, QEMU, Terraform\\
  {\bf Tools:} Helix, Kakoune, (Neo)Vim\\

  {\bf Social skills:} Worked in multiple pairs and teams, participated in team-building activities. Working with other people is a strong point.

  \section{PERSONAL PROJECTS}

  {\bf \href{https://github.com/fufexan/dotfiles}{Dotfiles}} \hfill \textit{2021 - Present}\\
  \begin{itemize}
    \item Managing my own desktop machines running NixOS through the use of Git and Flakes.
    \item Every machine is accessible everywhere through Tailscale VPN.
    \item Useful configurations accumulated over the years.
  \end{itemize}


  {\bf \href{https://github.com/fufexan/infra}{Infrastructure}} \hfill \textit{2022 - Present}\\
  \begin{itemize}
    \item Server management provisioned through Terraform, running multiple services as modules on NixOS. Accessible through Tailscale VPN.
    \item \textbf{arm-server:} Oracle ARM VPS running multiple services.
    \item \textbf{Home Server:} Older machine running various services for my family and I.
  \end{itemize}

  {\bf \href{https://github.com/fufexan/nix-gaming}{Nix Gaming}} \hfill \textit{2021 - Present}\\
  \begin{itemize}
    \item Repo hosting an ever-growing collection of games and gaming-related programs packaged for Nix.
  \end{itemize}

  {\bf Contributions}
  \begin{itemize}
    \item Maintainer of \href{https://github.com/hyprwm}{\textbf{Hyprland and the Hyprland ecosystem}}
    \item Maintainer for \href{https://github.com/nixos/nixpkgs}{\textbf{Nixpkgs}}
    \item Maintainer for \href{https://github.com/nix-community}{\textbf{Nix Community projects}}
  \end{itemize}

  \section{EDUCATION}
  {\bf Bachelor's degree in Electronics, Telecommunications \& Information Technology}, Technical University of Cluj-Napoca \hfill \textit{2021 - Present}\\
  {\bf High School diploma in Mathematics \& Informatics}, "Titu Maiorescu" National College, Aiud \hfill \textit{2017 - 2021}\\

  \section{DIPLOMAS}
  {\bf English Olympiad}
  \begin{itemize}
    \item 1st place, County Stage \hfill \textit{2016}
    \item 2nd place, County Stage \hfill \textit{2020}
    \item Mentions \hfill \textit{2017 - 2019}
  \end{itemize}
  {\bf Informatics Olympiad}, Participation \hfill \textit{2017 - 2018}\\
  {\bf OSEPI}, Participation \hfill \textit{2020}\\

  \section{VOLUNTEERING}
  \hspace{4mm}
  {\bf Romanian Red Cross} \hfill \textit{2018}
  \begin{itemize}
    \item Volunteered at the local subsidiary and participated in county-wide projects.
    \item Those projects included: fundraisers, orphanage visits, making \& selling handicrafts, donations.
  \end{itemize}

  \section{CERTIFICATIONS}
  \hspace{4mm}
  {\bf Digital Nation}
  \begin{itemize}
    \item \href{https://drive.google.com/file/d/15JN-Ko_CXP_WKGsrRxdQNzniaNkSrgTx/view}{\textbf{Certificate of Completion}}
    \item \href{https://drive.google.com/file/d/1Ahga9TNBsfRH_j3DBIsywD5D3XRbzElf/view}{\textbf{PHP Knowledge Certificate}}
  \end{itemize}
  \hspace{4mm}
  {\bf TUCN}
  \begin{itemize}
    \item {\textbf{Python Course}} - 3 ECTS credits
  \end{itemize}
\end{resume}
\end{document}
